---
title: "Group7 Project - Coffee Rating"
author: "Ece Gulkirpik, Johana Coronel, Mengyi Dong"
date: "10/8/2020"
output: html_document
---
```{r}
## Install tidytuesday package
library(tidyverse)
library(tidytuesdayR)
# Read data file
## coffee_rating
coffee_ratings <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2020/2020-07-07/coffee_ratings.csv')
```

1. Introduction - Ece


```{r}
## Summary statistics of the "Coffee Rating" dataset


```

2. Analysis
2.1 Total Rating Points for Each Country - Mengyi
We hope to compare the overall rating of different country and regions. To better visualize the data, we proposed to use a map chart with a choropleth world map. Choropleth map is a type of thematic map that usually used to represent an aggregate summary of a geographic characteristic. Here, we use a serial of color shades to represent the average/ mean overall score of coffees from different countries. Also, a summary table of the highest score, lowest score, and average score of each country is provided.
```{r}
## 2.1.1 Create a summary table with number of coffee rated, highest, lowest, and average rating score for each country.
ratingbycountry <- coffee_ratings %>%
  group_by(country_of_origin) %>%
  summarise(
    count = n(),
    highest_score = max(total_cup_points),
    lowest_score = min(total_cup_points),
    mean_score = mean(total_cup_points)
  )
write.table(ratingbycountry, file = "/Users/Mengyi/Box/CPSC441 R programming/Group-7 Project/data/Overall_Rating_by_Country.txt")

## 2.1.2 Creating a world map of coffee rating using choropleth map chart.
require(maps)
require(viridis)
theme_set(
  theme_void()
)
## Create a world map.
world_map <- map_data("world")
ggplot(world_map, aes(x = long, y = lat, group = group)) +
  geom_polygon(fill="lightgray", colour = "white")
```

2.2 Sensory Attributes of Coffee Species - Johana
Spider graph

```{r}
## Code for spider graph
```

2.3 The Effect of Type of Species, Altitude and Processing Method on Sensory Attributes - Ece
ANOVA
```{r}
## Code for ANOvA statistical analysis


```

3. Conclusion - Together


4. References


