---
title: "Group7 Project"
author: "Ece Gulkirpik, Johana Coronel, Mengyi Dong"
date: "10/8/2020"
output: html_document
---
Project guidelines
-Select the variables of interest and conduct the appropriate filters (Must include at least 3 variables)
-Provide summary statistics of the selected data
-Extract information from the data using [high quality] graphs
-Conduct a statistical analysis such as Analysis of Variance or Linear Regression
-Save the means from the selected variables as a text file.
-Post a selected graph on Twitter using the hashtags #tidytuesday and #RStat

```{r}
install.packages("tidytuesdayR")
# Read data file
## coffee_rating
coffee_ratings <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2020/2020-07-07/coffee_ratings.csv')

## or beer production
brewing_materials <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2020/2020-03-31/brewing_materials.csv')
beer_taxed <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2020/2020-03-31/beer_taxed.csv')
brewer_size <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2020/2020-03-31/brewer_size.csv')
beer_states <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2020/2020-03-31/beer_states.csv')
```



```{r}
##
```

